### 2023-03-05 manuscript.tex
Updating my information in the metadata [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/a177cf5c28b557f4befa7f1ad912f64e65101efb.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/a177cf5c28b557f4befa7f1ad912f64e65101efb/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4333442113

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/6855a7f181d90025efefe38a357366e9594bb35d/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/6855a7f181d90025efefe38a357366e9594bb35d}{SORTEE-Github-Hackathon/manuscript@6855a7f}
on 2023-03-05.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/a177cf5c28b557f4befa7f1ad912f64e65101efb/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/a177cf5c28b557f4befa7f1ad912f64e65101efb}{SORTEE-Github-Hackathon/manuscript@a177cf5}
on 2023-03-05.
